quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-20 paper-quollr.Rmd
Found a way to refer the Figure inside figure (need to map with figure label)

```{r limb-rmse, fig.cap="Assessing which of the 6 NLDR layouts on the limb muscle data is the better representation using RMSE for varying binwidth ($a_1$). Colour  used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-f). Layout d is perform well at large binwidth (where the binwidth is not enough to capture the data struture) and poorly as bin width decreases. Layout f is the best choice.", fig.pos='H'}

@@

```{r model-limb, fig.cap="Compare the published $2-\\text{D}$ layout (Figure \\@ref(fig:limb-rmse) b) and the $2-\\text{D}$ layout selected (Figure \\@ref(fig:limb-rmse) f) by RMSE plot (Figure \\@ref(fig:limb-rmse)) from the tSNE, UMAP, PHATE, TriMAP, and PaCMAP with different (hyper)parameters. The Limb muscle data ($n =  1067$) has seven close different shaped clusters in $10\\text{-}D$.", fig.pos='H', fig.width=15, fig.height=10, eval=knitr::is_latex_output()}

>>>>

```{r limb-rmse, fig.cap="Assessing which of the 6 NLDR layouts on the limb muscle data is the better representation using RMSE for varying binwidth ($a_1$). Colour  used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-f). Layout d is perform well at large binwidth (where the binwidth is not enough to capture the data struture) and poorly as bin width decreases. Layout f is the best choice.\\label{fig:limb-rmse}", fig.pos='H'}

@@

```{r model-limb, fig.cap="Compare the published $2-\\text{D}$ layout (Figure \\ref{fig:limb-rmse}b) and the $2-\\text{D}$ layout selected (Figure \\ref{fig:limb-rmse}f) by RMSE plot (Figure \\ref{fig:limb-rmse}) from the tSNE, UMAP, PHATE, TriMAP, and PaCMAP with different (hyper)parameters. The Limb muscle data ($n =  1067$) has seven close different shaped clusters in $10\\text{-}D$.", fig.pos='H', fig.width=15, fig.height=10, eval=knitr::is_latex_output()}

### 2025-05-20 paper-quollr.tex
Updated trimesh figure configurations
Changed the position of the figure
Found a way to refer the Figure inside figure (need to map with figure label)

\begin{figure}
\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/limb-rmse-1} \caption{Assessing which of the 6 NLDR layouts on the limb muscle data is the better representation using RMSE for varying binwidth ($a_1$). Colour  used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-f). Layout d is perform well at large binwidth (where the binwidth is not enough to capture the data struture) and poorly as bin width decreases. Layout f is the best choice.}\label{fig:limb-rmse}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/model-limb-1} \caption{Compare the published $2-\text{D}$ layout (Figure \\ref{fig:limb-rmse} b) and the $2-\text{D}$ layout selected (Figure \\ref{fig:limb-rmse} f) by RMSE plot (Figure \\ref{fig:limb-rmse}) from the tSNE, UMAP, PHATE, TriMAP, and PaCMAP with different (hyper)parameters. The Limb muscle data ($n =  1067$) has seven close different shaped clusters in $10\text{-}D$.}\label{fig:model-limb}
\end{figure}

>>>>

\begin{figure}[H]
\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/limb-rmse-1} \caption{Assessing which of the 6 NLDR layouts on the limb muscle data is the better representation using RMSE for varying binwidth ($a_1$). Colour  used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-f). Layout d is perform well at large binwidth (where the binwidth is not enough to capture the data struture) and poorly as bin width decreases. Layout f is the best choice.\label{fig:limb-rmse}}\label{fig:limb-rmse}
\end{figure}

\begin{figure}[H]
\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/model-limb-1} \caption{Compare the published $2-\text{D}$ layout (Figure \ref{fig:limb-rmse}b) and the $2-\text{D}$ layout selected (Figure \ref{fig:limb-rmse}f) by RMSE plot (Figure \ref{fig:limb-rmse}) from the tSNE, UMAP, PHATE, TriMAP, and PaCMAP with different (hyper)parameters. The Limb muscle data ($n =  1067$) has seven close different shaped clusters in $10\text{-}D$.}\label{fig:model-limb}
\end{figure}
